Parsing Tweets into Universal Dependencies

### 2017-12-16 paper.tex
finalize

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}

%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

Before turning to UD annotations, we (re)annotated the data with 
POS tags, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
In some cases,  non-corresponding tag conflicts arose between the UD English 
treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
\newcite{owoputi-EtAl:2013:NAACL-HLT}.  %\yicomment{The conflicts
                                %should refer to a {\bf
                                %noncorresponding tag} from that of
                                %gimpel to UDEnglish, cuz they dont
                                %have the same tagset.} 
In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

@@

\paragraph{Retweet construction.} Figure \ref{fig:non-syn-toks} shows
an example of the retweet construction (\emph{RT @coldplay :}).  This
might be treated as a verb phrase, with \emph{RT} as a verb and the
at-mention as an argument \yicomment{@coldplay seems not to be an
  object, could be some modifier like vocative, or some prepositional
  case (the tweets on/about coldplay)}\yjcomment{i am okey with
  current version} \nascomment{changed ``object'' to ``argument'' - better?}.
% \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
%\yjcomment{i wouldn't like the readers to think in this direction.}.
  This solution would lead to an uninformative root
word and, since this expression is idiomatic to Twitter, might create
unnecessary confusion for downstream applications aiming to identify
the main predicate(s) of a tweet.  We therefore treat the whole
expression as non-syntactic, including assigning the \emph{other}
(\texttt{X}) part of speech to both \emph{RT} and \emph{@coldplay},
attaching the at-mention to \emph{RT} with the \emph{discourse}
label and the colon to \emph{RT} with the \emph{punct}(uation) label,
and attaching \emph{RT} to the predicate of the following sentence.
%\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.

@@

\paragraph{Constructions handled by UD.}  A number of constructions
that are especially common in tweets are well handled by UD
conventions: ellipsis, irregular word orders, and paratactic phrases
and sentences 
not explicitly delineated by punctuation.

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is a vocative at-mention (sometimes a
signal that a tweet is a reply to a tweet by the mentioned user). % \yicomment{not necessary, can be just mentioning somebody. should be careful to say it. We can say this construction include 1. reply;  2. mention sb. Both cases are similar to general vocative proper noun case in standard texts. And we need to exclude at-mentions in Retweet Construction.}\yjcomment{i didn't see any difference between reply and mention, they all starts with a @username.}.
We
treat these at-mentions as vocative expressions, labeling them with
POS tag
\emph{proper noun} (\texttt{PROPN}) and attaching them to the
main predicate of the sentence it is within with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).\yjcomment{as Yi suggested, change ``following predicate'' to ``main ... within''}

@@

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
(840 unique tweets, 639/201 for training/test set), along with an 
additional 210 tweets sampled from the POS-tagged dataset of
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
The latter data source consists of 147.4M English tweets after being
filtered by the {\it lang} attribute in the tweet JSON and {\it
  langid.py} toolkit.\footnote{\url{https://github.com/saffsd/langid.py}}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\		 
% 		UD pipe v1.2 & 94.7 \\
		\hdashline
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
\citet{wang-EtAl:2017:Long6} show that the parser trained 
on the combination of UD\_English and English dialect (Singlish) treebank
outperform the one only on the dialect treebank.  Preliminary results
showed the same in our case \nascomment{added to address an open issue}, so 
we follow their work and trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training set
and tested on the \textsc{Tweebank v2} test set.% \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with the UD pipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
which has stronger representation power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}. We therefore consider existing POS taggers for tweets instead of developing our own.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
(both greedy and CRF variants), and 
\citet{ma-hovy:2016:P16-1}'s neural network tagger 
which achieves the state-of-the-art performance on PTB.
\citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
but their implementation works only with the PTB tagset
\nascomment{check here -- seems surprising to me, hopefully that's
  enough for reviewers}, so we exclude
it. % Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All compared systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific GloVe embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \citet{kong-EtAl:2014:EMNLP2014}'s parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses the biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system. \yjcomment{i briefly describ the compared systems.}
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\section{Conclusion}
We study the problem of parsing tweets into universal dependencies.
We adapt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2}, which has 3,550 tweets  and 55,607 tokens. We characterize the disagreements
among our annotators and argue that inherent ambiguity in this genre
makes
consistent annotation a challenge.  Using this new treebank,
we build a pipeline system to parse tweets into UD. We also 
propose a new method to distill an ensemble of 20 greedy parsers into a single one
to overcome annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.6  in LAS over a strong baseline
and outperforms other state-of-the-art parsers in both accuracy and speed.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}
\def\aclpaperid{214}
%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

Before turning to UD annotations, we (re)annotated the data with 
POS tags, for consistency with other UD efforts,
which adopt the universal POS tagset of \newcite{PETROV12.274}.
% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens. For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
In some cases,  non-corresponding tag conflicts arose between the UD English 
treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011}.  %\yicomment{The conflicts
                                %should refer to a {\bf
                                %noncorresponding tag} from that of
                                %gimpel to UDEnglish, cuz they dont
                                %have the same tagset.} 
In these cases, we always
conformed to UD, enabling consistency (e.g., when we exploit the
existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
rather than {\it conjunction} ({\tt CCONJ}).  
% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}

@@

\paragraph{Retweet construction.} Figure \ref{fig:non-syn-toks} shows
an example of the retweet construction (\emph{RT @coldplay :}).  This
might be treated as a verb phrase, with \emph{RT} as a verb and the
at-mention as an argument.
% \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
%\yjcomment{i wouldn't like the readers to think in this direction.}.
  This solution would lead to an uninformative root
word and, since this expression is idiomatic to Twitter, might create
unnecessary confusion for downstream applications aiming to identify
the main predicate(s) of a tweet.  We therefore treat the whole
expression as non-syntactic, including assigning the \emph{other}
(\texttt{X}) part of speech to both \emph{RT} and \emph{@coldplay},
attaching the at-mention to \emph{RT} with the \emph{discourse}
label and the colon to \emph{RT} with the \emph{punct}(uation) label,
and attaching \emph{RT} to the predicate of the following sentence.
%\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.

@@

\paragraph{Constructions handled by UD.}  A number of constructions
that are especially common in tweets are handled by UD
conventions: ellipsis, irregular word orders, and paratactic phrases
and sentences 
not explicitly delineated by punctuation.

@@

\paragraph{Vocative at-mentions.}  Another idiomatic construction on
Twitter is a vocative at-mention (sometimes a
signal that a tweet is a reply to a tweet by the mentioned user). % \yicomment{not necessary, can be just mentioning somebody. should be careful to say it. We can say this construction include 1. reply;  2. mention sb. Both cases are similar to general vocative proper noun case in standard texts. And we need to exclude at-mentions in Retweet Construction.}\yjcomment{i didn't see any difference between reply and mention, they all starts with a @username.}.
We
treat these at-mentions as vocative expressions, labeling them with
POS tag
\emph{proper noun} (\texttt{PROPN}) and attaching them to the
main predicate of the sentence it is within with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).

@@

\subsubsection{Data Collection}
{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
(840 unique tweets, 639/201 for training/test set), along with an 
additional 210 tweets sampled from the POS-tagged dataset of
\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
The latter data source consists of 147.4M English tweets after being
filtered by the {\it lang} attribute in the tweet JSON and {\it
  langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 96.6 \\
		 Twokenizer & 94.4 \\		 
% 		UD pipe v1.2 & 94.7 \\
		\hdashline
		UD pipe v1.2 & 97.3 \\
	 	our bi-LSTM tokenizer & 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
\citet{wang-EtAl:2017:Long6} show that the parser trained 
on the combination of UD\_English and English dialect (Singlish) treebank
outperform the one only on the dialect treebank.  Preliminary results
showed the same in our case, so 
we follow their work and trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English training set
and tested on the \textsc{Tweebank v2} test set.% \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} systems are rule-based systems and were not adapted
to the UD tokenization scheme.
The UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with the UD pipe, we use LSTM
instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
which has stronger representation power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results indicate the value of statistical modeling
in tokenization for informal texts.

@@

Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}. We therefore consider existing POS taggers for tweets instead of developing our own.
On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
(both greedy and CRF variants), and 
\citet{ma-hovy:2016:P16-1}'s neural network tagger 
which achieves the state-of-the-art performance on PTB.
\citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
but their implementation works only with the PTB tagset, so we exclude
it. % Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
 %and also two bi-LSTM systems similar
%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
All compared systems were re-trained on the combination of the UD\_English and 
\textsc{Tweebank v2} training sets. We use Twitter-specific GloVe embeddings released by
\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}

@@

\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
the stack LSTM with {\sc TweeboParser} (the system 
of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
in the CoNLL 2017 evaluations, due to
 \citet{dozat-qi-manning:2017:K17-3}.
 \citet{kong-EtAl:2014:EMNLP2014}'s parser is a graph-based
parser with lexical features and word cluster and it uses dual decomposition
for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
but includes character-based word representation and uses the biaffine classifier
to predict if an attachment exists between two words.
Both of the compared systems require superlinear runtime due to graph-based parsing. 
They are re-trained on the same data as our
system.
Our baseline lags behind by nearly two LAS
points but runs faster than both of them.

@@

\section{Conclusion}
We study the problem of parsing tweets into universal dependencies.
We adapt the UD guidelines to cover 
special constructions in tweets and create
the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
among our annotators and argue that inherent ambiguity in this genre
makes
consistent annotation a challenge.  Using this new treebank,
we build a pipeline system to parse tweets into UD. We also 
propose a new method to distill an ensemble of 20 greedy parsers into a single one
to overcome annotation noise without sacrificing efficiency.
Our parser achieves an improvement of 2.6  in LAS over a strong baseline
and outperforms other state-of-the-art parsers in both accuracy and speed.
